---
title: "Report: Summarized course evaluation"
output:
  word_document: 
    reference_docx: Style_of_report.docx
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
# The source function calls the R script containing the data ("data.R" needs to be saved in same folder as the RMarkdown report)
    source("data.R") 

# Packages needed
  library(knitr)
  library(pander)
  library(tidyverse)
```


```{r echo=FALSE}
# ------------------------------------------------------------------------------------- #
        # WHICH COURSE or MODULE DO YOU WANT TO EVALUATE ?
 
#         -> insert course code between the " ",

              course = "2019_LSAMPLE"

# ------------------------------------------------------------------------------------- #
               
# dataframe on module level (average scores across all participants of that module)
      selection <- filter(data_courses, course_code == course) 
      selection_modules <- filter(data_modules, course_code == course)
```
<br/><br/>

<center>
**Title of the course:** `r selection$course_title`  
**Course code:** `r selection$course_code`  
**Course ID:** `r selection$courseID`  
**Duration of the whole course:** `r selection$startdate` until `r selection$enddate` (`r selection$duration` days)   
**location:** `r selection$location`  
**lecturer:** `r selection$lecturer_all`  
**Number of participants:** `r selection$npart`  
**Average response rate across modules:** `r round(selection$responserate*100)`%  
</center>

<br/>

## Interpretation of scores

The survey measures the following dimensions: *Relevance of the topic*, *Teaching quality*, *Quality of material*, *Satisfaction with facilities*, *Level of difficulty* and the *Skill development*.  
  
Scores are given on a scale from 0-100.
  
**Courses should obtain average scores above 80.**    

```{r echo=FALSE, warning=FALSE}
#scores
tables <- c("Strongly disagree"= 0, 
                     "Disagree" = 20,
                     "Somehow disagree"= 40,
                     "Somehow agree"= 60,
                     "Agree" = 80,
                     "Strongly agree" = 100)

panderOptions("table.style","simple")
panderOptions("table.alignment.default","left")
panderOptions("table.split.table",Inf)
panderOptions("table.split.cells", 30)
  pander(tables)
```

<br/><br/>
<br/><br/>
<br/><br/>

## Summary  

The following figure shows the average scores across all modules of the course. 
  
```{r echo=FALSE, fig.width=8, warning=FALSE}
  # Summary plot
      plot <- selection[c('relevance',"TQ_f","TQlect_f","TQmat_f","facil_f","skills")] %>%
          dplyr::rename(
                       "Relevance of the topics" = relevance,
                       "Overall teaching quality" = TQ_f,
                       "- Teaching quality: Lecturer performance" = TQlect_f,
                       "- Teaching quality: Course material" = TQmat_f,
                       "Satisfaction with the facilities" = facil_f,
                       "Skill development" = skills)  %>%
          gather(plot) 

            ggplot(plot, aes(x=plot, y=value)) +
               geom_bar(stat = "identity", fill="#787878")  +
               coord_flip(ylim = c(0, 100)) +
               geom_hline(yintercept=80, linetype="dashed") +
              xlab(NULL) +
              ylab(NULL) +
              theme(axis.text.y = element_text(size = 12)) +
              theme(axis.text.x = element_text(size = 12))
```

The following table summarises the average scores across all modules in this course and gives a reference score (the average score on this dimension across all courses in the database).  
  
```{r echo=FALSE, fig.width=8, warning=FALSE}
  # Summary table with reference score (across all courses of the same category)
    Database_averages <- data_categories %>% 
      filter(course_cat == selection$course_cat) %>%   
      select(c("relevance","TQ_f","TQlect_f","TQmat_f","facil_f","skills", "lev_difficulty")) 
    
    table <- selection[c('relevance',"TQ_f","TQlect_f","TQmat_f","facil_f", "skills","lev_difficulty")] %>%
      bind_rows(Database_averages) %>%
      dplyr::rename("Average relevance of the topics" = relevance,
                     "Overall teaching quality" = TQ_f,
                     "- Teaching quality: Lecturer performance" = TQlect_f,
                     "- Teaching quality: Course material" = TQmat_f,
                     "Satisfaction with the facilities" = facil_f,
                     "Level of difficulty" = lev_difficulty,
                     "Perceived skill development" = skills) %>% 
      mutate_if(is.numeric, round,0) %>%
      t %>% as.data.frame %>%
          dplyr::rename("Current course score (0-100)" = V1,
                        "Database average score (0-100)" = V2) 

  # Print table
    panderOptions("table.style","simple")
    panderOptions("table.alignment.default","left")
    panderOptions("table.split.table",Inf)
    panderOptions("table.split.cells", 30)
        pander(table)
    ```

## Satisfaction with the facilities

```{r echo=FALSE, warning=FALSE}
#table for satisfaction with the facilities
tables <- selection[c("Q_ffac1","Q_ffac2","Q_ffac3","Q_ffac4", "facil_f")]
  tables <- dplyr::rename(tables, 
        "Item 1" = Q_ffac1,
        "Item 2" = Q_ffac2,
        "Item 3" = Q_ffac3,
        "Item 4" = Q_ffac4,
        "Average" = facil_f) %>%
    round %>%
  gather(tables) 
  tables <- dplyr::rename(tables,
                    "Evaluated statement" = tables,
                    "Score (0 - 100)   " = value) 

panderOptions("table.style","simple")
panderOptions("table.alignment.default","left")
panderOptions("table.split.table",Inf)
panderOptions("table.split.cells", 30)
  pander(tables)
```

## List of all modules in this course       

```{r echo=FALSE, fig.width=10}
# list of all modules of this course
table <- selection_modules[c("module_code","lecturer",
                        "skills","lev_difficulty","relevance","TQ_f","TQlect_f","TQmat_f")] %>%
      dplyr::rename("Module" = module_code,
                    "Lecturer" = lecturer,
                    "Relevance of topic" = relevance,
                    "Difficulty" = lev_difficulty,
                    "Skill development" = skills,
                    "Overall teaching quality" = TQ_f,
                    "- Lecturer performance" = TQlect_f,
                    "- Quality of teaching material" = TQmat_f ) %>% 
      mutate_if(is.numeric, round)    

panderOptions("table.style","simple")
panderOptions("table.alignment.default","left")
panderOptions("table.split.table",Inf)
  pander(table)
```
