---
title: "Report: Module evaluation"
output:
  word_document: 
    reference_docx: Style_of_report.docx
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
# The source function calls the R script containing the data ("data.R" needs to be saved in same folder as the RMarkdown report)
    source("data.R") 

# Packages needed
  library(knitr)
  library(pander)
  library(tidyverse)
```

```{r echo=FALSE}
# ------------------------------------------------------------------------------------- #
        # WHICH COURSE or MODULE DO YOU WANT TO EVALUATE ?
 
#       -> define the course and module, 
#           course: insert the course code between the " ",
#           module: insert the module code between the " ",
#                   if the course has NO MODULES (e.g. short term courses), insert "No"

              course = "2019_LSAMPLE"
              module = "A1" 

# ------------------------------------------------------------------------------------- #
              
 # creates a dataframe with evaluation data for the selected module (or course)             
    if (module == "No" | module == "no") {
        selection <- filter(data_courses, course_code == course)
          sel_part <- filter(data, course_code == course)} else {
        selection <- filter(data_modules, course_module == (str_c(course, module, sep="_")))
          sel_part <- filter(data, course_module == (str_c(course, module, sep="_")))} 

      # fixes errors with strings in open answers
        sel_part <- mutate_at(sel_part, 
            vars(starts_with("OA")), str_replace_all, "\\r|\\n|\\#|\\_|\\*|\\**|\\##", "")
        sel_part <- mutate_at(sel_part, 
            vars(starts_with("OA")), str_replace_all, "\\-", ".")
```
<br/><br/>

<center>
**Title of the module:** `r selection$module_title`  
**Module code:** `r selection$course_module`  
**Course ID:** `r selection$courseID`  
**Duration of the whole course:** `r selection$startdate` until `r selection$enddate` (`r selection$duration` days)   
**location:** `r selection$location`  
**lecturer:** `r selection$lecturer`  
**Number of participants:** `r selection$npart`  
**Response rate:** `r round(selection$responserate*100)`%  
</center>

## Interpretation of scores

The survey measures the following dimensions: *Relevance of the topic*, *Teaching quality*, *Quality of material*, *Satisfaction with facilities*, *Level of difficulty* and the *Skill development*.  
  
Scores are given on a scale from 0-100.
  
**Courses should obtain average scores above 80.**    
  
```{r echo=FALSE}
#scores
tables <- c("Strongly disagree"= 0, 
                     "Disagree" = 20,
                     "Somehow disagree"= 40,
                     "Somehow agree"= 60,
                     "Agree" = 80,
                     "Strongly agree" = 100)

panderOptions("table.style","simple")
panderOptions("table.alignment.default","left")
panderOptions("table.split.table",Inf)
panderOptions("table.split.cells", 30)
  pander(tables)
```
  
Courses should obtain average scores **above 80.**    

## Summary

```{r echo=FALSE, warning=FALSE, fig.width=8, warning=FALSE}
# Summary table
    table_summary <- selection[c("TQ_f","TQlect_f","TQmat_f","skills",'relevance',"lev_difficulty")] %>%
      dplyr::rename("Overall teaching quality" = TQ_f,
                    "- Teaching quality: Lecturer performance" = TQlect_f,
                    "- Teaching quality: Course material" = TQmat_f,
                   "Perceived skill development" = skills,
                   "Relevance of the topic" = relevance,
                   "Level of difficulty" = lev_difficulty) %>%
      mutate_if(is.numeric, round,0) %>%
      gather(tables) %>% 
          dplyr::rename("Dimension" = tables,
                        "Score (0 - 100)" = value) 

# Summary plot
  plot_summary <- table_summary %>%
      filter(Dimension!="Level of difficulty") %>%
      dplyr::rename(Score = "Score (0 - 100)")
    plot_summary$Score <- as.numeric(plot_summary$Score)

ggplot(plot_summary, aes(x=Dimension, y=Score)) +
    geom_bar(stat = "identity", fill="#787878")  +
    coord_flip(ylim = c(0, 100)) +
    geom_hline(yintercept=80, linetype="dashed") +
    xlab(NULL) +
    ylab(NULL) +
    theme(axis.text.y = element_text(size = 12)) +
    theme(axis.text.x = element_text(size = 12))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# Table for summary (currently disabled, because the plot shows the summary values good enough)
    panderOptions("table.style","simple")
    panderOptions("table.alignment.default","left")
    panderOptions("table.split.table",Inf)
    panderOptions("table.split.cells", 30)
      pander(table_summary)
```

## Teaching quality

### Lecturer performance

```{r echo=FALSE, warning=FALSE}
#table for Lecturer performance
tables <- selection[c("Q_flec1","Q_flec2","Q_flec3","Q_flec4","Q_flec5","Q_flec6",
                       "Q_flec7","TQlect_f")]
  tables <- dplyr::rename(tables, 
        "Item 1" = Q_flec1,
        "Item 2" = Q_flec2,
        "Item 3" = Q_flec3,
        "Item 4" = Q_flec4,
        "Item 5" = Q_flec5,
        "Item 6" = Q_flec6,
        "Item 7" = Q_flec7,
        "Average" = TQlect_f) %>%
    round %>%
  gather(tables) 
  tables <- dplyr::rename(tables,
                    "Evaluated statement" = tables,
                    "Score (0 - 100)   " = value) 

  panderOptions("table.style","simple")
  panderOptions("table.alignment.default","left")
  panderOptions("table.split.table",Inf)
  panderOptions("table.split.cells", 30)
    pander(tables)
```

#### Feedback on the lecturer performance  

```{r echo=FALSE, warning=FALSE}
# open answers for lecturer performance
tables <- na.omit(sel_part["OA_flec"])
      tables <- dplyr::rename(tables, 
            "-" = OA_flec) %>%
      gather(tables) 
      tables <- dplyr::rename(tables,
                        " " = tables,
                        "What would you tell the lecturers to improve their performance?" = value) 
    
          panderOptions("table.style","multiline")
          panderOptions("table.alignment.default","left")
            pander(tables)
```

### Quality of the course material

```{r echo=FALSE, warning=FALSE}
#table for quality of course material
tables <- selection[c("Q_fmat1","Q_fmat2","TQmat_f")]
  tables <- dplyr::rename(tables, 
        "Item 8" = Q_fmat1,
        "Item 9" = Q_fmat2,
        "Average" = TQmat_f) %>%

    round %>%
  gather(tables) 
  tables <- dplyr::rename(tables,
                    "Evaluated statement" = tables,
                    "Score (0 - 100)   " = value) 

panderOptions("table.style","simple")
panderOptions("table.alignment.default","left")
panderOptions("table.split.table",Inf)
panderOptions("table.split.cells", 30)
  pander(tables)
```

#### Comments on the course material  

```{r echo=FALSE, warning=FALSE}  
# open answers for course material
tables <- na.omit(sel_part["OA_fmat"])
      tables <- dplyr::rename(tables, 
            "-" = OA_fmat) %>%
      gather(tables) 
      tables <- dplyr::rename(tables,
                        " " = tables,
                        "How would you change the course material to improve the quality?" = value) 
    
          panderOptions("table.style","multiline")
          panderOptions("table.alignment.default","left")
            pander(tables)
```

## Perceived skill development

```{r echo=FALSE, warning=FALSE}
#table for skill development
tables <- selection[c("Q_skill1","Q_skill2","Q_skill3","skills")]
  tables <- dplyr::rename(tables, 
        "Item 10" = Q_skill1,
        "Item 11" = Q_skill2,
        "Item 12" = Q_skill3,
        "Average" = skills) %>%
    round %>%
  gather(tables) 
  tables <- dplyr::rename(tables,
                    "Evaluated statement" = tables,
                    "Score (0 - 100)   " = value) 

panderOptions("table.style","simple")
panderOptions("table.alignment.default","left")
panderOptions("table.split.table",Inf)
panderOptions("table.split.cells", 30)
  pander(tables)
```

## Relevance of the topic  

```{r echo=FALSE, warning=FALSE}
#table for relevance
tables <- selection[c("Q_rel1","Q_rel2","Q_rel3",'relevance')]
  tables <- dplyr::rename(tables, 
         "Item 13" = Q_rel1,
         "Item 14" = Q_rel2,
         "Item 15" = Q_rel3,
         "Average" = relevance) %>%
  round %>%
  gather(tables) 
  tables <- dplyr::rename(tables,
                    "Evaluated statement" = tables,
                    "Score (0 - 100)   " = value) 
  
panderOptions("table.style","simple")
panderOptions("table.alignment.default","left")
panderOptions("table.split.table",Inf)
panderOptions("table.split.cells", 30)
  pander(tables)
```

#### Comments on the relevance of the module 

```{r echo=FALSE, warning=FALSE}
# open answers for relevance
tables <- na.omit(sel_part["OA_rel"])
      tables <- dplyr::rename(tables, 
            "-" = "OA_rel") %>%
      gather(tables) 
      tables <- dplyr::rename(tables,
                        " " = tables,
                        "Why do you think the topic of the course (or module) might not be relevant"= value) 
          
          panderOptions("table.style","multiline")
          panderOptions("table.alignment.default","left")
            pander(tables)
```
  
    
## Level of difficulty

In general, the participants found the module to be **`r selection$lev_difficulty`**   
*Index:  1 = "very easy", 2 = "easy", 3 = "somewhat easy", 4 = "somewhat difficult", 5 = "difficult", 6 = "very difficult"* 

```{r echo=FALSE, warning=FALSE}
#table for level of dificulty scores
tables <- selection[c("lQ_dif1" ,"lQ_dif2","difficulty")] %>%
  mutate_if(is.numeric, round,2) %>%
  dplyr::rename("Item 16" = lQ_dif1,
                "Item 17" = lQ_dif2,
                "Average" = difficulty) %>%
        gather(tables) %>% 
          dplyr::rename("Evaluated statement" = tables,
                        "Score (1 - 6)" = value) 
  
panderOptions("table.style","simple")
panderOptions("table.alignment.default","left")
panderOptions("table.split.table",Inf)
panderOptions("table.split.cells", 30)
  pander(tables)
```

## Satisfaction with the facilities  

```{r echo=FALSE, warning=FALSE}
#table for satisfaction with the facilities
tables <- selection[c("Q_ffac1","Q_ffac2","Q_ffac3","Q_ffac4", "facil_f")]
  tables <- dplyr::rename(tables, 
        "Item 18" = Q_ffac1,
        "Item 19" = Q_ffac2,
        "Item 20" = Q_ffac3,
        "Item 21" = Q_ffac4,
        "Average" = facil_f) %>%
    round %>%
  gather(tables) 
  tables <- dplyr::rename(tables,
                    "Evaluated statement" = tables,
                    "Score (0 - 100)   " = value) 

if (!is.na(selection$facil_f)) {
    panderOptions("table.style","simple")
    panderOptions("table.alignment.default","left")
    panderOptions("table.split.table",Inf)
    panderOptions("table.split.cells", 30)
      pander(tables)
} else {
  pander(c( "In this module the satisfaction with facilities has not been evaluated. It will only appear in the last module report of this course and in the course summary report."))
}
```
  
## Open answers and comments

#### Strengths  

```{r echo=FALSE, warning=FALSE}
# open answers for overall strengths
    tables <- na.omit(sel_part[c(as.character("OA_strength"))]) 
      tables <- dplyr::rename(tables, 
            "-" = OA_strength) %>%
      gather(tables) 
     tables <- dplyr::rename(tables,
                        " " = tables,
                        "Please identify what you consider to be the strengths of this course (or module):" =value)
          panderOptions("table.style","multiline")
          panderOptions("table.alignment.default","left")
            pander(tables)
 
```
  
#### Weaknesses  

```{r echo=FALSE, warning=FALSE}  
# open answers for overall weaknesses
    tables <- na.omit(sel_part[c(as.character("OA_weakness"))]) 
      tables <- dplyr::rename(tables, 
            "-" = OA_weakness) %>%
    gather(tables)
    tables <- dplyr::rename(tables,
                        " " = tables,
                        "Please identify area(s) where you think the course (or module) could be improved:" =value)
           
          panderOptions("table.style","multiline")
          panderOptions("table.alignment.default","left")
            pander(tables)
```
  

#### Comments  

```{r echo=FALSE, warning=FALSE}   
# other comments
    
tables <- na.omit(sel_part[(as.character("OA_com"))]) 
  tables <- dplyr::rename(tables, 
            "-" = OA_com) %>%
      gather(tables) 
      tables <- dplyr::rename(tables,
                              "-" = tables,
                        "Do you have any other comments?" = value) 
    
          panderOptions("table.style","multiline")
          panderOptions("table.alignment.default","left")
            pander(tables)
```
  