---
title: "Report: Evaluation of the year"
output:
  word_document: 
    reference_docx: Style_of_report.docx
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
# The source function calls the R script containing the data ("data.R" needs to be saved in same folder as the RMarkdown report)
    source("data.R") 

# Packages needed
  library(knitr)
  library(pander)
  library(tidyverse)
```

```{r echo=FALSE}
# ------------------------------------------------------------------------------------#
        # FOR WHICH YEAR DO YOU WANT TO GET A SUMMARY ?
#
#         define the year, just insert the year in " " below

              Year = "2019"

# ------------------------------------------------------------------------------------- #
            
  # dataframe with all course data from the selected year
    selection <- filter(data_years, year == Year)
```
<br/><br/>

<center>
**Sumary Report for: **  `r selection$year`   
**Total Number of participants: **  `r selection$npart_total`  
**Average response rate: **  `r round(selection$responserate*100)`%  
</center>

## Interpretation of scores
  
The survey measures the following dimensions: *Relevance of the topic*, *Teaching quality*, *Quality of material*, *Satisfaction with facilities*, *Level of difficulty* and the *Skill development*.  
  
Scores are given on a scale from 0-100.
  
**Courses should obtain average scores above 80.**    

```{r echo=FALSE, warning=FALSE}
#scores
tables <- c("Strongly disagree"= 0, 
                     "Disagree" = 20,
                     "Somehow disagree"= 40,
                     "Somehow agree"= 60,
                     "Agree" = 80,
                     "Strongly agree" = 100)

panderOptions("table.style","simple")
panderOptions("table.alignment.default","left")
panderOptions("table.split.table",Inf)
panderOptions("table.split.cells", 30)
  pander(tables)
```


## Summary for `r selection$year` (Average scores across all face-to-face and e-Learning courses)  

```{r echo=FALSE, warning=FALSE, fig.width=10}
#Summary plot
plot <- selection %>%
    select('relevance',"TQ_f","TQlect_f","TQmat_f","facil_f", "skills","lev_difficulty") %>%
    dplyr::rename(
                 "Overall Teaching quality" = TQ_f,
                 "Lecturer performance" = TQlect_f,
                 "Course material" = TQmat_f,
                 "Satisfaction with facilities" = facil_f,
                 "Relevance" = relevance,
                 "Level of difficulty" = lev_difficulty,
                 "Skill development" = skills) %>%
      mutate_if(is.numeric, round,0) %>%
        gather(table) %>%
            dplyr::rename("Dimension" = table,
                          "Score (0 - 100)" = value) 
  
plot <- plot %>%
  filter(Dimension!="Level of difficulty") %>%
  dplyr::rename(Score = "Score (0 - 100)") 
plot$Score <- as.numeric(plot$Score)

    ggplot(plot, aes(x=Dimension, y=Score)) +
      geom_bar(stat = "identity", fill="#787878")  +
      coord_flip(ylim = c(0, 100)) +
      geom_hline(yintercept=80, linetype="dashed") +
      xlab(NULL) +
      ylab(NULL) +
      theme(axis.text.y = element_text(size = 12)) +
      theme(axis.text.x = element_text(size = 12))
```
  
## Comparison with previous years  

```{r echo=FALSE, warning=FALSE}
table <- data_years %>%
    dplyr::select("year",'relevance',"TQ_f","TQlect_f","TQmat_f",
                  "facil_f", "skills","lev_difficulty")  %>%
      mutate_if(is.numeric, round,0) %>%
      t %>% as.data.frame 

columnnames <- c("year","Relevance","Overall Teaching quality","Lecturer performance",
                 "Course material","Satisfaction with facilities",
                 "Level of difficulty","Skill development") %>%
              as.data.frame

table <-  bind_cols(columnnames,table) %>%
  dplyr::rename("Dimension" = ".") 

panderOptions("table.style","simple")
panderOptions("table.alignment.default","left")
panderOptions("table.split.table",Inf)
panderOptions("table.split.cells", 30)
  pander(table)
```

## Overall teaching quality  

```{r echo=FALSE, warning=FALSE, fig.width=11, fig.height=5}
# Bubble plot for teaching quality
plot <- data_courses %>%
  mutate(TQ = rowMeans(data_courses[,c("TQ_f","TQ_el")], na.rm=TRUE)) %>%
  mutate_at("course_cat", funs(factor)) %>%
  mutate_at("npart", funs(as.numeric)) 

ggplot(plot, aes(x=startdate, y=TQ)) +
        geom_point(aes(size=npart,colour = course_cat)) +
        scale_size_continuous(range=c(5,14)) +
        ylim(0,100) +
        labs(x = 'Startdate of the course', y = 'Teaching quality (0-100)',
             colour = 'Course category', size='Number of participants') 
```
  
## Perceived skill development  

```{r echo=FALSE, warning=FALSE, fig.width=11, fig.height=5}
# Bubble plot for perceived skill development
plot <- data_courses %>%
  mutate_at("course_cat", funs(factor)) %>%
  mutate_at("npart", funs(as.numeric)) 

ggplot(plot, aes(x=startdate, y=skills)) +
        geom_point(aes(size=npart,colour = course_cat)) +
        scale_size_continuous(range=c(5,14)) +
        ylim(0,100) +
        labs(x = 'Startdate of the course', y = 'Perceived skill development (0-100)',
             colour = 'Course category', size='Number of participants') 
```

## List of all courses    

```{r echo=FALSE, warning=FALSE, fig.width=10}
# list of all courses
table <- data_courses[c("course_code","startdate", "courseID", "npart","course_cat","year",
                        "location","lecturer_all","TQ_f",
                        "skills","lev_difficulty","relevance","facil_f")] %>%
  filter(year == Year) %>%
    select(-year) %>%
        dplyr::rename("Course" = course_code,
                      "Startdate" = startdate,
                      "course ID" = courseID,
                      "course category" = course_cat,
                      "number participants" = npart,
                      "location" = location,
                      "lecturer" = lecturer_all,
                      "Skill development" = skills,
                      "difficulty" = lev_difficulty,
                      "Relevance of topic" = relevance,
                      "Teaching quality" = TQ_f,
                      "satisfaction facilities" = facil_f) %>% 
        mutate_if(is.numeric, round,1)    

panderOptions("table.style","simple")
panderOptions("table.alignment.default","left")
panderOptions("table.split.table",Inf)
  pander(table)
```